This chapter shows the results of the simulations done with the framework shown in ch. \ref{ch:methodology} as well as discussing the results.
The chapter is mainly divided into two sections, the first explaining the configuration of the simulation as well as results depicted by graph-data.
The second section focuses on discussing the results in terms of the reason they have certain values and graphs, as well as a comparison between the different simulations and discovery of correlations and behavioural similarities.

\section{Experimental Results}
As stated in the chapter introduction, this section covers the results of the simulations. 
Even though the simulator supports a wide variety of different configurations, three main simulation groups chosen for this particular study.
The first group considers different connection port configurations for the robots.
The second simulation group varies the environment that the robots spend their life time in.
The third and final simulation group aims to observe the affect of local communication between the robots in a self-assembly structure(the implementation is shown in sec. \ref{sec:local_comm}).
The two first simulation groups targets to contribute to the three main self-assembly mechanisms discussed in ch. \ref{ch:background}(Self-assembly Architectures, Hardware Mechanisms and Assembly Protocols).
The local communication simulation group aims to study the affect giving the robots the ability to perform simple communication between the robots in a group.

\subsection{Port Configuration}
The first group of simulations that were done was varying the number of connection ports of the robots and their configuration.
These simulations where done such that one could record and discuss the impact of connections between the robots.
In more detail, this group of experiments where conducted such that one could record:

\begin{itemize}
	\item How the number of ports affected the general performance of the system based on the number of ports.
	\item If there is any noticeable difference in the self-assembly architecture.
	\item In what way the port configuration promotes self-assembly, both in therms of the sizes of the different robot groups, and the number of groups.
	\item How the port configuration affect the fitness of the experiment, in terms of convergence and final result.
\end{itemize}

The goal of running these simulations is to make correlations between its results to show how configuring the hardware mechanism can affect a self-assembly system.
 
For this group of simulations, the most relevant statistics will be the difference between group actions versus single robot actions.
The following pages show the recorded data for simulations using, 2 connection ports, 3 connection ports and 4 connection ports.



\newpage
\pagestyle{plain}

\input{chapters/graph-wrappers/2-ports-wrapper.tex}

\newpage

\input{chapters/graph-wrappers/3-ports-wrapper.tex}

\newpage

\input{chapters/graph-wrappers/4-ports-wrapper.tex}

\newpage
\pagestyle{main}

\subsection{Environment Difficulty}
The motivation for this experiment is to observe how changing the difficulty of the environment affects the evolved behaviour.
For the experiment two environment difficulties were constructed, one easier and one more difficult.
These environment difficulties were then used in the simulations so that the impact of the evolutionary pressure could be recorded and discussed.
More specifically the experiments were constructed to investigate how differing environment difficulties affect the following properties of the evolved behaviour.

\begin{itemize}
	\item The amount of robot groups formed through self-assembly, and the number of robots in each group.
	\item How the energy gathering behaviour is affected. Whether the robots prefer gathering energy individually, or as robot groups. 
	\item How the environment difficulty affects the fitness of the experiment, in terms of convergence and final result.
\end{itemize}


The environment difficulty is modified by varying the following simulation parameters.
The initial energy level the robots, the maximum amount of energy each robot can be charged with, the amount of food in the environment, and the number of predators present in the simulation.
Table \ref{tab:environment-difficulty} presents the simulation parameters that are varied for the environments.

\begin{table}[H]
	\centering
	\label{tab:environment-difficulty}
	\begin{tabular}{|c|c|c|c|c|}
		\hline  & Predators & Initial energy & Food items & Maximum energy \\ 
		\hline Easy environment & 4 & 8000 & 25 & 10000 \\ 
		\hline Hard environment & 7 & 6000 & 20 &8000 \\ 
		\hline 
		
	\end{tabular} 
	\caption{The simulation parameters for the environments.}
\end{table}

The results were obtained by running 20 simulation trials for each difficulty.
\subsubsection{Easy Environment}

\newpage
\pagestyle{plain}

\input{chapters/graph-wrappers/easy-wrapper.tex}

\newpage

\paragraph{Environmental limiting factor}
%The robots have two main threats in the environments presented, starvation and getting killed by predators.
%From figure \ref{fig:easy-robots-starved} and figure \ref{fig:hard-robots-starved} one can see that the amount of robots %dying from starvation is approximately the same.
%The robots in the easy environment receive more energy from food, and there is more food available.
%This does not seem to impact the amount of robots dying from starvation, which may indicate that the avaliable energy

\subsubsection{Difficult Environment}

\newpage

\input{chapters/graph-wrappers/hard-wrapper.tex}

\newpage
\pagestyle{main}

\subsection{Local Communication}

\section{Discussion}

































