\documentclass[a4paper,12pt,twoside,openright]{book}

\usepackage{afterpage}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{booktabs}
\renewcommand{\arraystretch}{1.2} 
\usepackage{verbatim}
\usepackage{float}
\usepackage{pgfplots}
\usepackage{subcaption}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{datatool}
\usepackage{url}
\usepackage{hyperref}
\usepackage{filecontents}
\usepackage[toc,page]{appendix}
\usepackage[Lenny]{fncychap}
\restylefloat{table}
\title{Self-assembly mechanisms for evolutionary robotics}
\author{Eirik Jakobsen\\ Christopher Tannum}
\date{December 2015}

\usepackage[lmargin=35mm,rmargin=35mm,tmargin=37mm,bmargin=40mm]{geometry}

%custom commands

\input{chapters/commands/graphwrapperthree.tex}
\input{chapters/commands/graphwrappertwo.tex}

\makeatletter
\DeclareRobustCommand*\textsubscript[1]{%
	\@textsubscript{\selectfont#1}}
\def\@textsubscript#1{%
	{\m@th\ensuremath{_{\mbox{\fontsize\sf@size\z@#1}}}}}
\makeatother

% --
\floatstyle{plaintop}
\restylefloat{table}

\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}

\fancypagestyle{main}{%
  	\fancyhead{}
	\fancyfoot{}
	\fancyfoot[LE,RO]{\thepage}

	\fancyhead[R]{\small\nouppercase\leftmark}
	\fancyhead[L]{\small\nouppercase\rightmark}

	\renewcommand{\footrulewidth}{0.4pt}
	\renewcommand{\headrulewidth}{0.4pt}
}

\fancypagestyle{start}{%
  	\fancyhead{}
	\fancyfoot{}
}

\fancypagestyle{plain}{%
  	\fancyhead{}
	\fancyfoot{}
  	\renewcommand{\headrulewidth}{0pt}
  	\renewcommand{\footrulewidth}{0.4pt}
  	\fancyfoot[LE,RO]{\thepage}
}

\DeclareCaptionType{captioneq}[][List of equations]
\captionsetup[captioneq]{labelformat=empty}

\begin{document}

\pagestyle{start}

\frontmatter
\pagestyle{plain}


\chapter*{\begin{center} \begin{normalsize} \textbf{Abstract} \end{normalsize} \end{center} }
\vspace{-2.5cm}
In recent study, an increasing amount of time has been spent researching complex systems. The reason for this is an increasing need for solving complex problems where the traditional Von Neumann architecture lacks sufficient efficiency. 
A specific complex system which has been growing in popularity
is a system of swarm robots. 
Introducing evolutionary principles in such systems makes an attempt at collective computation, from simple elements, to resolve complex problems. 
To further add functionality to such systems, self-organizing techniques, such as self-assembly, have been introduced. 
Because of the lack of research literature within this paradigm, there are few comparisons of the different implementations of self-assembly mechanisms.
This thesis outlines some mechanisms of self-assembly and explores the positive and negative implications these may have on evolutionary self-assembling robots.
The results of the experiments conducted in this thesis show that self-assembly mechanisms such as the connection hardware and introducing local communication can influence the system's ability to self-assemble, and the behaviour of the self-assembled group.

\chapter*{\begin{center} \begin{normalsize} \textbf{Sammendrag} \end{normalsize} \end{center} }
\vspace{-2.5cm}
I nyere forskning har en {\o}kende innsats blitt brukt til {\aa} forske p{\aa} komplekse systemer. 
Grunnen til dette, er et {\o}kende behov for {\aa} l{\o}se komplekse problemer der den tradisjonelle Von Neumann arkitekturen mangler tilstrekkelig effektivitet.
Et spesifikt komplekst system som har v{\ae}rt i {\o}kende popularitet er et system av sverm roboter.
Ved introdusering av evolusjon{\ae}re prinsipper i slike systemer gj{\o}r man et fors{\o}k p{\aa} kollektiv beregning fra enkle elementer, for {\aa} l{\o}se komplekse problemer.
For {\aa} legge til ytterligere funksjonalitet til slike systemer har selvorganiserende teknikker, for eksempel selvmontering, blitt introdusert.
P{\aa} grunn av mangel p{\aa} forskningslitteraturen innen dette paradigmet, er det f{\aa} sammenligninger av de forskjellige implementeringer av selvmonterende mekanismer.
Denne avhandlingen beskriver noen mekanismer for selvmontering og utforsker de positive og negative konsekvenser disse kan ha p{\aa} evolusjon{\ae}re selvmonterende roboter.
Resultatene av fors{\o}kene utf{\o}rt i denne avhandlingen viser at selvmonteringsmekanismer, som for eksempel tilkoblingsmaskinvare og innf{\o}ring av lokal kommunikasjon, kan p{\aa}virke systemets evne til {\aa} selvmontere, og oppf{\o}rselen til den selvmonterte gruppen.

\chapter*{Preface}
\vspace{-2cm}
This master thesis is written at the Department of Computer and Information Science at NTNU during the spring semester of 2016. 
During their 8th semester, students are exposed to a number of different projects which are provided by the IDI faculty and professors at NTNU.
These projects are open to interpretation by the students to enable their creativity.
This thesis builds on a research project conducted during the autumn of 2015, which had the following project description:

\begin{center}
	
	\textit{"Self-assembly mechanisms are useful in collective robotics in order to allow a group of robots to cross obstacles that a single robot could not cross. Another use of such mechanism is the drag heavy objects by multiple robots. In the last years,  multiple mechanisms have been proposed in the literature. The first task of the student will be to list these mechanisms find the relevant axes to classify the self-assembly mechanisms of the literature. The second task will be to compare these mechanisms. More specifically, an evolutionary algorithm will be selected for its ability to learn behaviours in groups of robots. Additionally, a task will be selected or designed for its proper level of challenge (that can be addressed thanks to self-assembly). Finally, the algorithm will be used on the task with the various mechanisms located, and comparisons will be made on the difficulties to evolve behaviours using self-assembly."\\}
	
\end{center}

From the researched project during 2015, several interesting research scopes were discovered.
An initial experiment was outlined during the project which was elaborated and continued throughout this thesis.
Exploring the different mechanisms and behaviours of swarm-robotics became the foundation of this thesis.

Special thanks to:

\begin{itemize}
	
	\item Kazi Shah Nawaz Ripon for extensive help in forming this report, supplementing theoretical foundation and imperative guidance.
	
	\item Jean-Marc Montanier for comprehensive help during the research project of fall 2015 which prompted the writing of this thesis
	
	\item Pauline Catriona Haddow for supplying this project and supplying contact with excellent supervisors.

\end{itemize}

\tableofcontents

\newpage
\listoffigures
\newpage
\listoftables

\mainmatter
\pagestyle{main}

\raggedbottom

\chapter{Introduction}
\label{ch:introduction}
\input{chapters/introduction}
\clearpage

\chapter{Background}
\label{ch:background}
\input{chapters/background}
\clearpage

\chapter{Methodology}
\label{ch:methodology}
\input{chapters/methodology}
\clearpage

\chapter{Results and Discussion}
\label{ch:results_and_discussion}
\input{chapters/results-and-discussion}
\clearpage

\chapter{Conclusion}
\label{ch:conclusion}
\input{chapters/conclusion}
\clearpage

\nocite{*}

\bibliographystyle{abbrv}

\bibliography{references} 

\begin{appendices}
	\label{ch:appendices}
	\input{chapters/appendices}
\end{appendices}

\end{document}