\vspace*{\fill}

\insertresultgraphs{chapters/generated-graphs/2-ports/fitness-out-2-ports.tex}{chapters/generated-graphs/3-ports/fitness-out-3-ports.tex}{chapters/generated-graphs/4-ports/fitness-out-4-ports.tex}{The \textbf{fitness} results from connection port simulations}{fitness}

Figure \ref{fig:results-ports-fitness} show the results for achieved fitness for the port configuration simulations.
The two and four connection port results are very similar where the four connection port performs slightly better with an average fitness of about 0.2 on generation 1 rising to about 0.5 on generation 150. 
The three connection port simulation performs worse, concerning fitness, in every aspect compared to the other port configurations.

\vspace*{\fill}
\newpage
\vspace*{\fill}

\insertresultgraphs{chapters/generated-graphs/2-ports/group_distribution-out-2-ports.tex}{chapters/generated-graphs/3-ports/group_distribution-out-3-ports.tex}{chapters/generated-graphs/4-ports/group_distribution-out-4-ports.tex}{The \textbf{group distribution} results from connection port simulations}{group-distribution}

Figure \ref{fig:results-ports-group-distribution} represents the distribution of group sizes formed during simulation.
The size of the circles indicates the number of groups formed.
The two and four connection port simulations have more groups of all sizes with the exception of a single group of size five which was formed from the three connection port simulation.
The four connection port simulation formed larger groups than the two connection port simulation.

\vspace*{\fill}
\newpage
\vspace*{\fill}

\insertresultgraphs{chapters/generated-graphs/2-ports/number_of_groups-out-2-ports.tex}{chapters/generated-graphs/3-ports/number_of_groups-out-3-ports.tex}{chapters/generated-graphs/4-ports/number_of_groups-out-4-ports.tex}{The \textbf{number of groups} results from connection port simulations}{number-of-groups}

Figure \ref{fig:results-ports-number-of-groups} shows the number of groups which were formed in the different simulations.
It is seen that the results of the two and four connection port simulations are very similar where the only notable difference is that the four connection port results seem to converge at a faster rate.
The three connection port results are quite poor, having few groups throughout the trial.

\vspace*{\fill}
\newpage
\vspace*{\fill}

\insertresultgraphs{chapters/generated-graphs/2-ports/robots_eaten-out-2-ports.tex}{chapters/generated-graphs/3-ports/robots_eaten-out-3-ports.tex}{chapters/generated-graphs/4-ports/robots_eaten-out-4-ports.tex}{The \textbf{robots eaten} results from connection port simulations}{robots-eaten}

Figure \ref{fig:results-ports-robots-eaten} shows the number of robots which were eaten by predators during simulation.
The four connection port simulation performs best, but only slightly better than the two connection port robots.
The four connection port results converges faster and has slightly better results at the end of the simulation.
The three connection port results are quite poor in comparison where a lot more robots are consumed by predators.

\vspace*{\fill}
\newpage
\vspace*{\fill}


\insertresultgraphs{chapters/generated-graphs/2-ports/robots_starved-out-2-ports.tex}{chapters/generated-graphs/3-ports/robots_starved-out-3-ports.tex}{chapters/generated-graphs/4-ports/robots_starved-out-4-ports.tex}{The \textbf{robots starved} results from connection port simulations}{robots-starved}

Figure \ref{fig:results-ports-robots-starved} shows the number of robots starved each generation.
The results for two and four connection port simulations are very similar where the average number of robots starved is about four at the final generation(150).
The three connection port simulation performs slightly better on these results where the average number of starved robots is slightly less than 3.
The three connection port simulation performs best on this result because most of the robots have been consumed by a predator before they die of starvation.

\vspace*{\fill}
\newpage
\vspace*{\fill}


\insertresultgraphs{chapters/generated-graphs/2-ports/energy_consumed_by_group-out-2-ports.tex}{chapters/generated-graphs/3-ports/energy_consumed_by_group-out-3-ports.tex}{chapters/generated-graphs/4-ports/energy_consumed_by_group-out-4-ports.tex}{The \textbf{energy consumed by group} results from connection port simulations}{energy-consumed-by-group}

Figure \ref{fig:results-ports-energy-consumed-by-group} shows the energy consumed by groups of robots during simulation.
From these results, it can be viewed that the results containing 2 and four connection ports are very similar with an average result of about 60 energy items consumed at generation 150.
The three port configuration performs a lot worse with a result of about ten energy items consumed at generation 150.
The results are correlated with the results obtained from the number of groups formed in the simulation(figure \ref{fig:number-of-groups-3-ports}).


\vspace*{\fill}
\newpage
\vspace*{\fill}


\insertresultgraphs{chapters/generated-graphs/2-ports/energy_consumed_by_robot-out-2-ports.tex}{chapters/generated-graphs/3-ports/energy_consumed_by_robot-out-3-ports.tex}{chapters/generated-graphs/4-ports/energy_consumed_by_robot-out-4-ports.tex}{The \textbf{energy consumed by robot} results from connection port simulations}{energy-consumed-by-robot}

Figure \ref{fig:results-ports-energy-consumed-by-robot} shows the total amount of energy which is consumed by robots which are not self-assembled.
All of the graphs have similar results and slopes, with the exception that the three connection port simulation performs worse.
The reason the average results of figure \ref{fig:energy-consumed-by-robot-2-ports} and \ref{fig:energy-consumed-by-robot-4-ports} flattens out and does not increase after around generation 30 is that more of the robots are self-assembling and hence is not tracked as a part of these results.
As the energy consumed is not decreasing because more robots are a part of groups, it can be deduced that more energy is consumed on a per robot basis.

\vspace*{\fill}
\newpage
\vspace*{\fill}


\insertresultgraphs{chapters/generated-graphs/2-ports/predators_eaten-out-2-ports.tex}{chapters/generated-graphs/3-ports/predators_eaten-out-3-ports.tex}{chapters/generated-graphs/4-ports/predators_eaten-out-4-ports.tex}{The \textbf{predators eaten} results from connection port simulations}{predators-eaten}

Figure \ref{fig:results-ports-predators-eaten} tracks the number of predators that have been eaten by robot groups. 
The four connection port simulation performs best and is correlated with having larger group sizes than the other port configuration shown in figure \ref{fig:group-distribution-4-ports}.
As the robot groups must be of at least size three to consume a predator, the results shown in this figure conform with the other results shown earlier.

\vspace*{\fill}
